---
title: "Biomarker ROC and AUC Power"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Biomarker ROC and AUC Power}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
library(ggpower)
```

## In plain English

You have a continuous biomarker and want to know whether it can **discriminate**
diseased from non-diseased subjects. ROC AUC summarizes that discrimination.
This vignette covers one-sample AUC vs chance (0.5) and two-sample AUC comparison.

## One-sample AUC vs null

```{r roc-one}
power_compute(
  "roc_auc_one",
  analysis = "a_priori",
  auc = 0.75,
  auc0 = 0.5,
  n_pos = 50,
  n_neg = 50,
  alpha = 0.05,
  power = 0.8,
  tails = "two"
)
```

## Compare two biomarkers

```{r roc-two}
power_compute(
  "roc_auc_two",
  analysis = "post_hoc",
  auc1 = 0.78,
  auc2 = 0.62,
  n1 = 80,
  n2 = 80,
  alpha = 0.05,
  tails = "two"
)
```

## Formula

Hanley-McNeil SE for one AUC; DeLong-style variance for two independent AUCs.
See [formula reference](formula-reference.html).

## Plot

Run the calculation in the **Biomarker Discovery** module to see the distribution
and sample-size curve.

## Related analyses

- [Diagnostic accuracy](biomarker-diagnostic-accuracy.html)
- [Differential expression](biomarker-differential-expression.html)
