---
title: "Choosing the Right Module"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Choosing the Right Module}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
library(ggpower)
```

## In plain English

Not every research question belongs in the same module. Use this guide to pick the
sidebar entry that matches your endpoint and study design.

## Decision guide

```{r modules, echo=FALSE}
data.frame(
  Question = c(
    "What sample size for a standard t test or ANOVA?",
    "Can my biomarker discriminate cases from controls (AUC)?",
    "Is my classifier sensitive and specific enough?",
    "Does a biomarker predict survival?",
    "How many patients for a Phase III superiority trial?",
    "Is treatment non-inferior to standard of care?",
    "Is a new formulation equivalent (bioequivalence)?",
    "Oncology single-arm Phase II with early stopping?"
  ),
  Module = c(
    "Power Workspace",
    "Biomarker Discovery",
    "Biomarker Discovery",
    "Biomarker Discovery",
    "Clinical Trials",
    "Clinical Trials",
    "Clinical Trials",
    "Clinical Trials"
  ),
  Example_test = c(
    "t_two_sample",
    "roc_auc_one",
    "diagnostic_acc",
    "cox_regression",
    "rct_superiority_continuous",
    "rct_noninferiority_binary",
    "rct_equivalence_continuous",
    "simon_two_stage"
  )
)
```

## Filter tests by module

```{r filter}
ggpower_tests(module = "biomarker")[, c("id", "label")]
```

```{r filter2}
ggpower_tests(module = "clinical")[, c("id", "label")]
```

## When NOT to switch modules

Stay in **Power Workspace** when you need specialized classical tests (McNemar,
tetrachoric correlation, Wilcoxon, etc.) even if the endpoint sounds clinical.

## Related analyses

- [Getting started with the GUI](getting-started-gui.html)
- [Choosing a power analysis](choosing-a-power-analysis.html)
