---
title: "Simon Two-Stage Design"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Simon Two-Stage Design}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
library(ggpower)
```

Simon optimal two-stage design for single-arm Phase II oncology trials.

## Formula

Stage-wise binomial operating characteristics under $p_0$ (null) and $p_1$ (target).

**Modes:** `post_hoc` and `sensitivity` only (no sample-size solver).

## Post hoc power

```{r example}
power_compute("simon_two_stage", "post_hoc", p0 = 0.2, p1 = 0.4,
              r1 = 4, r = 10, n1 = 20, n2 = 20, alpha = 0.05)
```

## Sensitivity — detectable response rate

```{r sens}
power_compute("simon_two_stage", "sensitivity", p0 = 0.2, r1 = 4, r = 10,
              n1 = 20, n2 = 20, alpha = 0.05, power = 0.8)
```

## Related

- [Scenario guide](scenario-guide.html) — design search not yet implemented
- [Binary endpoints](pharma-binary-and-count-endpoints.html)
