---
title: "Calculator"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Calculator}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
library(ggpower)
```

The **Calculator** module in `run_app()` evaluates distribution-function scripts.
The same engine is available as `ggpower_calculator()`.

## Basic arithmetic

```{r arith}
ggpower_calculator("2^3 + 1")
```

## Inverse normal

```{r zinv}
ggpower_calculator("zinv(0.975)")
```

## Noncentral t CDF

```{r nct}
ggpower_calculator("nctcdf(1.699127, 29, 3.423266)")
```

## Multi-line script

```{r multi}
ggpower_calculator("alpha <- 0.05
nctcdf(1.699127, 29, 3.423266)")
```

## Available helpers

Common functions: `zcdf`, `zinv`, `tcdf`, `tinv`, `fcdf`, `finv`, `chisqcdf`,
`chisqinv`, `ncfcdf`, `nctcdf`, `binomcdf`, and assignment with `<-`.

## Related

- [Getting started with the GUI](getting-started-gui.html)
- [Formula reference](formula-reference.html)
