---
title: "Correlation and z Tests"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Correlation and z Tests}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
library(ggpower)
```

z tests for correlations and GLM coefficients.

## Independent correlations

```{r indep}
q <- effect_size_q(0.75, 0.88)
power_compute("z_corr_independent", "post_hoc", q_effect = q,
              n1 = 51, n2 = 260, alpha = 0.05)
```

## Dependent correlations (common index)

```{r common}
power_compute("z_corr_dependent_common", "a_priori", rho_ab = 0.4,
              rho_ac = 0.2, rho_bc = 0.5, alpha = 0.05,
              power = 0.8, tails = "one")
```

## Dependent correlations (no common index)

```{r nocommon}
power_compute("z_corr_dependent_no_common", "post_hoc", rho_ab = 0.1,
              rho_cd = 0.2, rho_ac = 0.5, rho_ad = 0.4,
              rho_bc = -0.4, rho_bd = 0.8, n = 200)
```

## Exact correlation (Fisher-Z approximation)

```{r exactr}
power_compute("exact_correlation", "post_hoc", rho = 0.3, rho0 = 0,
              n = 50, alpha = 0.05, tails = "two")
```

## Tetrachoric correlation (approximation)

```{r tetra}
power_compute("z_tetrachoric", "post_hoc", rho = 0.4, n = 100, alpha = 0.05)
```

## Logistic regression

```{r logist}
power_compute("z_logistic", "a_priori", odds_ratio = 1.5, p0 = 0.5,
              alpha = 0.05, power = 0.95, total_n = 300,
              r2_other = 0, x_variance = 1)
```

## Poisson regression

```{r pois}
power_compute("z_poisson", "a_priori", exp_beta1 = 1.3,
              base_rate = 0.85, exposure = 1, alpha = 0.05,
              power = 0.95, r2_other = 0, x_variance = 0.25)
```

## Related

- [Logistic and Poisson](logistic-poisson.html)
- [Formula reference](formula-reference.html)
